Tampering Detection In Low-Power Smart Cameras

### 2015-06-18 paper.tex
Modificata immagine sequenze e modificata descrizione del dataset

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences.}
\label{fig:sequences}
\end{figure}

@@

We acquired two datasets: the first dataset contains  sequences of  frames taken from webcams monitoring urban areas (e.g., see Figure \ref{fig:sequences}(a)). 
The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
In the first dataset tampering was synthetically generated by blurring frames (see, Figure \ref{fig:sequences}(b)) or concatenating frames from different sequences depicting similar environments (see Figure \ref{fig:sequences}(c)). 
Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
At last we have considered $9$ different scenarios, with $10$ displacement events and $10$ blurring events each, for a total of $180$ tampering events.%\gi{una footnote dicendo sequences can be released upon request?}

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as

@@

where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (missed tampered frames), respectively, for a given value of $\gamma_l$ (or $\gamma_g$).

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 3-rd frame, created using gaussian filtering; \textbf{(c)} displacement event on 3-rd frame, created moving the crop of the original image from the center.}
\label{fig:sequences}
\end{figure}

@@

The considered dataset contains  sequences of  frames taken from webcams monitoring urban areas (e.g., see Figure \ref{fig:sequences}(a)), in which we've taken the central crop of each image (about $3/4$ of the original image). 
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
In order to have a wide and sound dataset, the tampering events have been made synthetically, blurring the frames by gaussian kernels (see, Figure \ref{fig:sequences}(b)) or moving the crop of the frames in order to simulate displacements (see Figure \ref{fig:sequences}(c)). 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
At last we have considered $8$ different scenarios, for a total of $24410$ frames considered, in which we've inserted $5\%$ of displacement events ($1224$ frames) and $5\%$ of blurring events ($1224$ frames).\footnote{Sequences can be released upon request}

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as

@@

where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (missed tampered frames), respectively, for a given value of $\gamma$.
